---
title: "Analysis"
author: "Amy Heather"
date: "`r Sys.Date()`"
output:
  github_document:
      toc: true
      html_preview: false
---

This notebook presents execution and results from:

* Base case analysis
* Scenario analysis
* Sensitivity analysis

The generated images are saved and then loaded, so that we view the image as saved (i.e. with the dimensions set in `ggsave()`). This also avoids the creation of a `_files/` directory when knitting the document (which would save all previewed images into that folder also, so they can be rendered and displayed within the output `.md` file, even if we had not specifically saved them). These are viewed using `include_graphics()`, which must be the last command in the cell (or last in the plotting function).

Some of these are used in the paper (`mock_paper.md`) - see below:

* **Figure 1:** `outputs/spread_arrivals.png`
* **Figure 2:** `outputs/scenario_nurse_util.png`
* **Figure 3:** `outputs/scenario_nurse_wait.png`
* **Figure 4:** `outputs/sensitivity_consult_time.png`

The run time is provided at the end of the notebook.

## Set up

Install the latest version of the local simulation package. If running sequentially, `devtools::load_all()` is sufficient. If running in parallel, you must use `devtools::install()`.

```{r}
devtools::load_all()
```

Import required packages.

```{r}
# nolint start: undesirable_function_linter.
library(dplyr, warn.conflicts = FALSE)
library(ggplot2)
library(knitr)
library(simmer, warn.conflicts = FALSE)
library(simulation)
library(tidyr, warn.conflicts = FALSE)
library(xtable)

options(dplyr.summarise.inform = FALSE)
# nolint end
```

Start timer.

```{r}
start_time <- Sys.time()
```

Define path to outputs folder.

```{r}
output_dir <- file.path("..", "outputs")
```

## Default run

Run with default parameters and save to `.csv`.

```{r}
# Print out default parameters
print(parameters())

# Run model
run_results <- runner(param = parameters())[["run_results"]]

# Preview results
head(run_results)

# Save results to csv
write.csv(run_results, file.path(output_dir, "base_run_results.csv"))
```

Can calculate overall results from across the replications as well...

```{r}
# Calculate average results
run_results %>%
  dplyr::select(!c(replication, arrivals)) %>%
  gather() %>%
  group_by(key) %>%
  reframe(mean = mean(value, na.rm = TRUE),
          std_dev = stats::sd(value, na.rm = TRUE),
          ci_lower = stats::t.test(value)[["conf.int"]][[1L]],
          ci_upper = stats::t.test(value)[["conf.int"]][[2L]])
```

## View spread of results across replication

```{r}
#' Plot spread of results from across replications, for chosen column.
#'
#' Generate figure, show it, and then save under specified file name.
#'
#' @param run_results The dataframe from the model results `run_results`.
#' @param column Name of column to plot.
#' @param x_label X axis label.
#' @param file Filename to save figure to.

plot_results_spread <- function(run_results, column, x_label, file) {

  # Generate plot
  p <- ggplot(run_results, aes(.data[[column]])) +
    geom_histogram(bins = 10L) +
    labs(x = x_label, y = "Frequency") +
    theme_minimal()

  # Save plot
  full_path <- file.path(output_dir, file)
  ggsave(filename = full_path, plot = p,
         width = 6.5, height = 4L, bg = "white")

  # View the plot
  include_graphics(full_path)
}
```

```{r}
plot_results_spread(run_results = run_results,
                    column = "arrivals",
                    x_label = "Arrivals",
                    file = "spread_arrivals.png")

plot_results_spread(run_results = run_results,
                    column = "mean_waiting_time_nurse",
                    x_label = "Mean wait time for nurse",
                    file = "spread_nurse_wait.png")

plot_results_spread(run_results = run_results,
                    column = "mean_serve_time_nurse",
                    x_label = "Mean length of nurse consultation",
                    file = "spread_nurse_time.png")

plot_results_spread(run_results = run_results,
                    column = "utilisation_nurse",
                    x_label = "Mean nurse utilisation",
                    file = "spread_nurse_util.png")
```

## Scenario analysis

```{r}
# Run scenario analysis
scenarios <- list(
  patient_inter = c(3L, 4L, 5L, 6L, 7L),
  number_of_nurses = c(5L, 6L, 7L, 8L)
)

scenario_results <- run_scenarios(scenarios, base_list = parameters())
```

```{r}
# Preview scenario results dataframe
print(dim(scenario_results))
head(scenario_results)
```

Example plot

```{r}
#' Plot results from different model scenarios.
#'
#' @param results Dataframe with results from each replication of scenarios.
#' @param x_var Name of variable to plot on X axis.
#' @param result_var Name of variable with results, to plot on Y axis.
#' @param colour_var Name of variable to colour lines with (or set to NULL).
#' @param xaxis_title Title for X axis.
#' @param yaxis_title Title for Y axis.
#' @param legend_title Title for figure legend.
#' @param path Path inc. filename to save figure to.
#'
#' @return Dataframe with the average results calculated.

plot_scenario <- function(results, x_var, result_var, colour_var, xaxis_title,
                          yaxis_title, legend_title, path) {
  # If x_var and colour_var are provided, combine both in a list to use
  # as grouping variables when calculating average results
  if (!is.null(colour_var)) {
    group_vars <- c(x_var, colour_var)
  } else {
    group_vars <- c(x_var)
  }

  # Calculate average results from each scenario
  avg_results <- results %>%
    group_by_at(group_vars) %>%
    summarise(mean = mean(.data[[result_var]]),
              std_dev = sd(.data[[result_var]]),
              ci_lower = t.test(.data[[result_var]])[["conf.int"]][[1L]],
              ci_upper = t.test(.data[[result_var]])[["conf.int"]][[2L]])

  # Generate plot - with or without colour, depending on whether it was given
  if (!is.null(colour_var)) {
    # Convert colour variable to factor so it is treated like categorical
    avg_results[[colour_var]] <- as.factor(avg_results[[colour_var]])
    # Create plot
    p <- ggplot(avg_results, aes(x = .data[[x_var]], y = mean,
                                 group = .data[[colour_var]])) +
      geom_line(aes(color = .data[[colour_var]])) +
      geom_ribbon(aes(ymin = .data[["ci_lower"]], ymax = .data[["ci_upper"]],
                      fill = .data[[colour_var]]), alpha = 0.1)
  } else {
    # Create plot
    p <- ggplot(avg_results, aes(x = .data[[x_var]], y = mean)) +
      geom_line() +
      geom_ribbon(aes(ymin = .data[["ci_lower"]], ymax = .data[["ci_upper"]]),
                  alpha = 0.1)
  }

  # Modify labels and style
  p <- p +
    labs(x = xaxis_title, y = yaxis_title, color = legend_title,
         fill = legend_title) +
    theme_minimal()

  # Save plot
  ggsave(filename = path, width = 6.5, height = 4L, bg = "white")

  # Return the results dataframe
  return(avg_results) # nolint: object_overwrite_linter
}
```

```{r}
# Define path
path <- file.path(output_dir, "scenario_nurse_wait.png")

# Calculate results and generate plot
result <- plot_scenario(
  results = scenario_results,
  x_var = "patient_inter",
  result_var = "mean_waiting_time_nurse",
  colour_var = "number_of_nurses",
  xaxis_title = "Patient inter-arrival time",
  yaxis_title = "Mean wait time for nurse (minutes)",
  legend_title = "Nurses",
  path = path
)

# View plot
include_graphics(path)
```

```{r}
# Define path
path <- file.path(output_dir, "scenario_nurse_util.png")

# Calculate results and generate plot
result <- plot_scenario(
  results = scenario_results,
  x_var = "patient_inter",
  result_var = "utilisation_nurse",
  colour_var = "number_of_nurses",
  xaxis_title = "Patient inter-arrival time",
  yaxis_title = "Mean nurse utilisation",
  legend_title = "Nurses",
  path = path
)

# View plot
include_graphics(path)
```

Example table.

```{r}
# Process table
table <- result %>%
  # Combine mean and CI into single column, and round
  mutate(mean_ci = sprintf("%.2f (%.2f, %.2f)", mean, ci_lower, ci_upper),
         nurses = sprintf("% s nurses", number_of_nurses)) %>%
  dplyr::select(patient_inter, nurses, mean_ci) %>%
  # Convert from long to wide format
  pivot_wider(names_from = nurses, values_from = mean_ci) %>%
  rename(`Patient inter-arrival time` = patient_inter)

# Convert to latex, display and save
table_latex <- xtable(table)
print(table_latex)
print(table_latex,
      comment = FALSE,
      file = file.path(output_dir, "scenario_nurse_util.tex"))
```

### Running a basic example (which can compare to Python template)

To enable comparison between the templates, this section runs the model with a simple set of base case parameters (matched to Python), and then running some scenarios on top of that base case.

```{r}
# Define the base param for this altered run
new_base <- parameters(
  patient_inter = 4L,
  mean_n_consult_time = 10L,
  number_of_nurses = 5L,
  # No warm-up (not possible in R, but set to 0 in Python)
  data_collection_period = 1440L,
  number_of_runs = 10L,
  cores = 1L
)

# Define scenarios
scenarios <- list(
  patient_inter = c(3L, 4L, 5L, 6L, 7L),
  number_of_nurses = c(5L, 6L, 7L, 8L)
)

# Run scenarios
compare_template_results <- run_scenarios(scenarios, new_base)
```

```{r}
# Preview scenario results dataframe
print(dim(compare_template_results))
head(compare_template_results)
```

```{r}
# Define path
path <- file.path(output_dir, "scenario_nurse_wait_compare_templates.png")

# Calculate results and generate plot
result <- plot_scenario(
  results = compare_template_results,
  x_var = "patient_inter",
  result_var = "mean_waiting_time_nurse",
  colour_var = "number_of_nurses",
  xaxis_title = "Patient inter-arrival time",
  yaxis_title = "Mean wait time for nurse (minutes)",
  legend_title = "Nurses",
  path = path
)

# View plot
include_graphics(path)

# Define path
path <- file.path(output_dir, "scenario_nurse_util_compare_templates.png")

# Calculate results and generate plot
result <- plot_scenario(
  results = compare_template_results,
  x_var = "patient_inter",
  result_var = "utilisation_nurse",
  colour_var = "number_of_nurses",
  xaxis_title = "Patient inter-arrival time",
  yaxis_title = "Mean nurse utilisation",
  legend_title = "Nurses",
  path = path
)

# View plot
include_graphics(path)
```

## Sensitivity analysis

Can use similar code to perform sensitivity analyses.

**How does sensitivity analysis differ from scenario analysis?**

* Scenario analysis focuses on a set of predefined situations which are plausible or relevant to the problem being studied. It can often involve varying multiple parameters simulatenously. The purpose is to understand how the system operates under different hypothetical scenarios.
* Sensitivity analysis varies one (or a small group) of parameters and assesses the impact of small changes in that parameter on outcomes. The purpose is to understand how uncertainty in the inputs affects the model, and how robust results are to variation in those inputs.

```{r}
# Run sensitivity analysis
consult <- list(mean_n_consult_time = c(8L, 9L, 10L, 11L, 12L, 13L, 14L, 15L))
sensitivity_consult <- run_scenarios(consult, base_list = parameters())
```

```{r}
# Preview result
head(sensitivity_consult)
```

```{r}
# Define path
path <- file.path(output_dir, "sensitivity_consult_time.png")

# Calculate results and generate plot
sensitivity_result <- plot_scenario(
  results = sensitivity_consult,
  x_var = "mean_n_consult_time",
  result_var = "mean_waiting_time_nurse",
  colour_var = NULL,
  xaxis_title = "Mean nurse consultation time (minutes)",
  yaxis_title = "Mean wait time for nurse (minutes)",
  legend_title = "Nurses",
  path = path
)

# View plot
include_graphics(path)
```

```{r}
# Process table
sensitivity_table <- sensitivity_result  %>%
  # Combine mean and CI into single column, and round
  mutate(mean_ci = sprintf("%.2f (%.2f, %.2f)", mean, ci_lower, ci_upper)) %>%
  # Select and rename columns
  dplyr::select(mean_n_consult_time, mean_ci) %>%
  rename(`Mean nurse consultation time` = mean_n_consult_time,
         `Mean wait time for nurse (95 percent confidence interval)` = mean_ci)

# Convert to latex, display and save
sensitivity_table_latex <- xtable(sensitivity_table)
print(sensitivity_table_latex)
print(sensitivity_table_latex,
      comment = FALSE,
      file = file.path(output_dir, "sensitivity_consult_time.tex"))
```

## NaN results

If patients are still waiting to be seen at the end of the simulation, or are still busy with the resource at the end of the simulation, they will have NaN results for `end_time` and `activity_time` (and so for the calculated nurse wait and activity times).

These patients are captured in the `wait_time_unseen` column in `arrivals`, and in the `count_unseen_nurse` and `mean_waiting_time_unseen_nurse` columns in `run_results`.

These patients will be ignored in calculation of metrics like mean time with nurse (as they don't get to see nurse) - but it's important we still have measures for those unseen, as lots of patients waiting at the end of the simulation reveals large backlogs in the system.

```{r}
# Set up parameters with short inter-arrival time
param <- parameters(patient_inter = 0.5)
print(param)

# Run replications
nan_experiment <- runner(param)
```

```{r}
nan_experiment[["arrivals"]] %>%
  arrange(replication, start_time) %>%
  tail()
```

```{r}
nan_experiment[["run_results"]][c(
  "replication", "count_unseen_nurse", "mean_waiting_time_nurse"
)]
```

```{r}
plot_results_spread(
  run_results = nan_experiment[["run_results"]],
  column = "count_unseen_nurse",
  x_label = "Patients still unseen by nurse at end of simulation (n)",
  file = "spread_nan_count_unseen.png"
)

plot_results_spread(
  run_results = nan_experiment[["run_results"]],
  column = "mean_waiting_time_nurse",
  x_label = "Mean nurse wait time by patients unseen at simulation end (min)",
  file = "spread_nan_wait_unseen.png"
)
```

## Calculate run time

```{r end_timer}
# Get run time in seconds
end_time <- Sys.time()
runtime <- as.numeric(end_time - start_time, units = "secs")

# Display converted to minutes and seconds
minutes <- as.integer(runtime / 60L)
seconds <- as.integer(runtime %% 60L)
cat(sprintf("Notebook run time: %dm %ds", minutes, seconds))
```
