---
title: "Choosing warm-up length"
author: "Amy Heather"
date: "`r Sys.Date()`"
output:
  github_document:
      toc: true
      html_preview: false
---

A suitable length for the warm-up period can be determined using the **time series inspection approach**. This involves looking at performance measures over time to identify when the system is exhibiting **steady state behaviour** (even though the system will never truly reach a "steady state").

If we simply plot the mean result over time, this would vary too much. Therefore, we plot the **cumulative mean** of the performance measure, and look for the point at which this **smoothes out and stabilises**. This indicates the point for the warm-up period to end.

This should be assessed when running the model using the base case parameters. If these change, you should reassess the appropriate warm-up period.

We should:

* Run the model with **multiple replications** (e.g. at least five).
* Use a **long run length** (i.e. 5-10 times actual planned run length).

The run time is provided at the end of the document.

Some of these figures are used in the paper (`mock_paper.md`) - see below:

* **Figure B.1:** `outputs/choose_param_time_series.png`

## Set-up

Install the latest version of the local simulation package. If running sequentially, `devtools::load_all()` is sufficient. If running in parallel, you must use `devtools::install()`.

```{r}
devtools::load_all()
```

Load required packages.

```{r}
# nolint start: undesirable_function_linter.
library(knitr)
library(simulation)

options(data.table.summarise.inform = FALSE)
options(dplyr.summarise.inform = FALSE)
# nolint end
```

Start timer.

```{r}
start_time <- Sys.time()
```

Define path to outputs folder.

```{r}
output_dir <- file.path("..", "outputs")
```

## Determining appropriate warm-up length

Run the model, ensuring multiple replications and a sufficient data collection period are used.

```{r}
data_collection_period <- 50000L

# Use default parameters, but with no warm-up, five replications, and the
# specified data collection period
param <- parameters(
  warm_up_period = 0L,
  data_collection_period = data_collection_period,
  number_of_runs = 5L
)
print(param)

# Run model
result <- runner(param)
```

Use the `time_series_inspection` function, which will find the cumulative mean over time (for each replication, and overall) and plot it, for three metrics:

* Mean wait time
* Mean service length
* Utilisation

```{r, fig.show='hide'}
path <- file.path(output_dir, "choose_param_time_series.png")

time_series_inspection(
  result = result,
  file_path = path,
  warm_up = 10000L
)
```

```{r}
include_graphics(path)
```

## Run time

```{r end_timer}
# Get run time in seconds
end_time <- Sys.time()
runtime <- as.numeric(end_time - start_time, units = "secs")

# Display converted to minutes and seconds
minutes <- as.integer(runtime / 60L)
seconds <- as.integer(runtime %% 60L)
cat(sprintf("Notebook run time: %dm %ds", minutes, seconds))
```
