---
title: "Generate expected results"
author: "Amy Heather"
date: "`r Sys.Date()`"
output:
  github_document:
      toc: true
      html_preview: false
---

This notebook is used to run a specific version of the model and save each results dataframe as a csv. These are used in `test-backtest.R` to verify that the model produces consistent results.

The `.Rmd` file is provided as it is possible that results may change due to alterations to the model structure and operations. Once it has been confirmed that changes are intentional and not any introduced errors, this script can be run to regenerate the `.csv` files used in the test.

The run time is provided at the end of this notebook.

## Set-up

Install the latest version of the local simulation package. If running sequentially, `devtools::load_all()` is sufficient. If running in parallel, you must use `devtools::install()`.

```{r}
devtools::load_all()
```

Load required packages.

```{r setup}
# nolint start: undesirable_function_linter.
library(simulation)
# nolint end
```

Start timer.

```{r start_timer}
start_time <- Sys.time()
```

Define path to expected results.

```{r path}
testdata_dir <- file.path("..", "tests", "testthat", "testdata")
```

## Base case

```{r}
# Define model parameters
param <- parameters(
  patient_inter = 4L,
  mean_n_consult_time = 10L,
  number_of_nurses = 5L,
  warm_up_period = 0L,
  data_collection_period = 80L,
  number_of_runs = 10L,
  cores = 1L
)
print(param)

# Run the replications
results <- runner(param)

# Arrivals
head(results[["arrivals"]])
write.csv(arrange(results[["arrivals"]], replication, start_time),
          file.path(testdata_dir, "base_arrivals.csv"),
          row.names = FALSE)

# Resources
head(results[["resources"]])
write.csv(results[["resources"]],
          file.path(testdata_dir, "base_resources.csv"),
          row.names = FALSE)

# Run results
head(results[["run_results"]])
write.csv(results[["run_results"]],
          file.path(testdata_dir, "base_run_results.csv"),
          row.names = FALSE)
```

## Model with a warm-up period

```{r}
# Define model parameters
param <- parameters(
  patient_inter = 4L,
  mean_n_consult_time = 10L,
  number_of_nurses = 5L,
  warm_up_period = 40L,
  data_collection_period = 80L,
  number_of_runs = 10L,
  cores = 1L
)

# Run the replications
results <- runner(param)[["run_results"]]

# Preview
head(results)

# Save to csv
write.csv(results, file.path(testdata_dir, "warm_up_results.csv"),
          row.names = FALSE)
```

## Scenario analysis

```{r}
# Define model parameters
param <- parameters(
  patient_inter = 4L,
  mean_n_consult_time = 10L,
  number_of_nurses = 5L,
  data_collection_period = 80L,
  number_of_runs = 3L,
  cores = 1L
)

# Run scenario analysis
scenarios <- list(
  patient_inter = c(3L, 4L),
  number_of_nurses = c(6L, 7L)
)
scenario_results <- run_scenarios(scenarios, base_list = param)

# Preview
head(scenario_results)

# Save to csv
write.csv(scenario_results, file.path(testdata_dir, "scenario_results.csv"),
          row.names = FALSE)
```

## Running the simulation when attempting to determine an appropriate number of parameters

The `confidence_interval_method` and `ReplicationsAlgorithm` should return the same results, so we will just run one to use in the back tests.

```{r}
# Specify parameters (so consistent even if defaults change)
param <- parameters(
  patient_inter = 4L,
  mean_n_consult_time = 10L,
  number_of_nurses = 5L,
  warm_up_period = 0L,
  data_collection_period = 80L
)

# Run the confidence_interval_method()
rep_results <- confidence_interval_method(
  replications = 15L,
  desired_precision = 0.1,
  metric = "mean_serve_time_nurse"
)

# Preview results
head(rep_results)

# Save to csv
write.csv(rep_results, file.path(testdata_dir, "choose_rep_results.csv"),
          row.names = FALSE)
```

## Calculate run time

```{r end_timer}
# Get run time in seconds
end_time <- Sys.time()
runtime <- as.numeric(end_time - start_time, units = "secs")

# Display converted to minutes and seconds
minutes <- as.integer(runtime / 60L)
seconds <- as.integer(runtime %% 60L)
cat(sprintf("Notebook run time: %dm %ds", minutes, seconds))
```
