---
title: "Logs"
author: "Amy Heather"
date: "`r Sys.Date()`"
output:
  github_document:
      toc: true
      html_preview: false
---

Logs will describe events during the simulation. Simmer has built-in functionality to generate logs, which can be activated by setting `verbose` as TRUE.

Logs will output lots of information, so they are best used when running the simulation for a short time with few patients. For example, to illustrate how a simulation work, or to support debugging.

## Set up

Install the latest version of the local simulation package. If running sequentially, `devtools::load_all()` is sufficient. If running in parallel, you must use `devtools::install()`.

```{r}
devtools::load_all()
```

Start timer.

```{r}
start_time <- Sys.time()
```

## Simulation run with logs printed to the console

We use the built-in simmer logging functionality. Within our `model` function, we accept the parameters:

* `log_to_console` - whether to print the activity log to the console.
* `log_to_file` - whether to save the activity log to a file.
* `file_path` - path to save log to file.

Here, we will print to console and save to file:

```{r}
log_file <- file.path("..", "outputs", "logs", "log_example.log")

param <- parameters(
  patient_inter = 6L,
  mean_n_consult_time = 8L,
  number_of_nurses = 1L,
  data_collection_period = 30L,
  number_of_runs = 1L,
  cores = 1L,
  log_to_console = TRUE,
  log_to_file = TRUE,
  file_path = log_file
)

verbose_run <- model(run_number = 0L, param = param)
```

If we import the log file, we'll see it contains the same output:

```{r}
log_contents <- readLines(log_file)
print(log_contents, sep = "\n")
```

### Interpreting the simmer log messages

#### Example A: `patient0`

The patient arrives at 1.10422 and requests a nurse. There is one available (`SERVE`) so the consultation begins (`Timeout`).

```
[5] "  1.10422 |   arrival: patient0         |  activity: Seize            | nurse, 1, 0 paths"
[6] "  1.10422 |  resource: nurse            |   arrival: patient0         | SERVE"
...
[10] " 1.10422 |   arrival: patient0         |  activity: Timeout          | function()"  
```

The consultation finishes at 2.26987, and the patient leaves:

```
[14] "   2.26987 |   arrival: patient0         |  activity: Release          | nurse, 1"
[15] "   2.26987 |  resource: nurse            |   arrival: patient0         | DEPART"
[16] "   2.26987 |      task: Post-Release     |          :                  | "
```

#### Example B: `patient2`

The patient arrives at 4.5594, requests a nurse and enters a queue (`ENQUEUE`).

```
[13] "   1.94299 |    source: patient          |       new: patient2         | 4.5594"             
...
[21] "    4.5594 |   arrival: patient2         |  activity: Seize            | nurse, 1, 0 paths"
[22] "    4.5594 |  resource: nurse            |   arrival: patient2         | ENQUEUE"
```

A nurse becomes available at 25.3823 (`SERVE`) so consultation begins (`Timeout`).

```
[39] "   25.4296 |  resource: nurse            |   arrival: patient2         | SERVE"
...                                                                                          
[42] "   25.4296 |   arrival: patient2         |  activity: Timeout          | function()"
```

However, there are no further entries for that patient as the simulation ends before the consultation ends.

### Compare with recorded results

The logs will align with the recorded results of each patient.

```{r}
arrange(verbose_run[["arrivals"]], start_time)
```

## Customising the log messages

The `simmer` package allows us to add additional log messages using the `_log()` function.

Here, we take our simmer code from `model.R` but set `verbose = TRUE`. We can then add additional `_log()` messages within the patient trajectory.

You may find this helpful for interpreting the log messages (for example, with the addition of emojis to make different activities more distinct).

```{r}
# Set the seed
set.seed(0L)

env <- simmer("simulation", verbose = FALSE)

# Define the patient trajectory
patient <- trajectory("appointment") %>%
  simmer::log_("🚶 Arrives.") %>%
  seize("nurse", 1L) %>%
  set_attribute("nurse_serve_start", function() now(env)) %>%
  set_attribute("nurse_serve_length", function() {
    rexp(n = 1L, rate = 1L / param[["mean_n_consult_time"]])
  }) %>%
  simmer::log_(function() {
    paste0("🩺 Nurse consultation begins (length: ",
           round(get_attribute(env, "nurse_serve_length"), 5L), ")")
  }) %>%
  timeout(function() get_attribute(env, "nurse_serve_length")) %>%
  release("nurse", 1L) %>%
  simmer::log_("🚪 Leaves.")

env <- env %>%
  add_resource("nurse", param[["number_of_nurses"]]) %>%
  add_generator("patient", patient, function() {
    rexp(n = 1L, rate = 1L / param[["patient_inter"]])
  }) %>%
  simmer::run(param[["data_collection_period"]])
```

## Calculate run time

```{r end_timer}
# Get run time in seconds
end_time <- Sys.time()
runtime <- as.numeric(end_time - start_time, units = "secs")

# Display converted to minutes and seconds
minutes <- as.integer(runtime / 60L)
seconds <- as.integer(runtime %% 60L)
cat(sprintf("Notebook run time: %dm %ds", minutes, seconds))
```
